\texttt{Davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-10-01 paper/main.tex

The \texttt{Davos} package supports reproducible research by providing
a novel, lightweight system for sharing notebook-based code. It
expands on Python's ``batteries included'' philosophy to enable running shared
notebooks with no setup required, and defines a simple, self-documenting format for
specifying dependencies in the spirit of the ``literate programming'' paradigm Jupyter notebooks promote.
But perhaps the most exciting uses of the \texttt{Davos} package are those
that we have \textit{not} yet considered or imagined. We hope that the
research and scientific Python communities will find \texttt{Davos} to provide a convenient
means of managing project dependencies to facilitate code sharing and collaboration. We
also hope that some of the more advanced applications of our package
might lead to new insights or discoveries.

>>>>

The \texttt{Davos} package supports reproducible research by providing
a novel, lightweight system for sharing notebook-based code. It
expands on Python's ``batteries included'' philosophy to enable running shared
notebooks with no setup required, and defines a simple, self-documenting format for
specifying dependencies in keeping with the ``literate programming'' paradigm that Jupyter notebooks support.
We designed \texttt{Davos} to fill a niche we believe will help facilitate contributing to and engaging with open science resources.
But perhaps the most exciting uses of the \texttt{Davos} package are those
that we have \textit{not} yet considered or imagined. We hope that the
research and scientific Python communities will find \texttt{Davos} to provide a convenient
means of managing project dependencies to facilitate code sharing and collaboration. We
also hope that some of the more advanced applications of our package
might lead to new insights or discoveries.
